MINOS Handover Plots

### 2024-09-06 minos/validation/handovers.Rmd

out.path <- here::here('output', 'default_config/')
#out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)
#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
```

>>>>

out.path <- here::here('output', 'default_config/')
# out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline',
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)

# base.dat <- read_singular_local_out(out.path, 'ChildPovertyReduction',
#                                     drop.dead = TRUE,
#                                     drop.zero.weight = TRUE)

#base.dat <- read_singular_local_out(out.path, 'goodHeatingDummy', drop.dead = TRUE)
```
